---
title: "Titanic presentation"
author: "Iain Morgan"
date: "9 feb 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)

titData <- as.data.frame(Titanic)

titData <- spread(titData,Survived,Freq)
titData <- titData %>% mutate(Prob = Yes / (No + Yes))
titData <- titData %>% unite(Sex.Age, Sex, Age, sep = " ")
titData$Prob <- round(titData$Prob * 100,0)
```

## What is this about?

This brief presentation will be looking at the survival rates of the passengers on the RMS Titanic.

- Of the 2224 passengers on board, more than 1500 died in the disaster
- The vessel was not equipped with enough lifeboats to accommodate the entire complement
- Many of the 2nd and 3rd class passengers had difficulty reaching the boats

## Survival rate of passengers by Class, Sex and Age

```{r,echo=FALSE, warning=FALSE}

p <- plot_ly(
  data = titData,
  x = ~Sex.Age,
  y = ~Prob,
  color = ~Class,
  type = "scatter",
  mode = "markers",
  size = ~Prob,
  text = ~paste(Class, 'class',Sex.Age, '<br>', Prob, '% survived')) %>%
  layout(
    title = "Survival probability of passengers on the RMS Titanic",
    xaxis = list(title = "Passenger sex and age", titlefont = "f"),
    yaxis = list(title = "Probability of survival", titlefont = "f")
      )
p
```

## Conclusions

From the data, we can see:

- 1st and 2nd class passengers had a higher probability of survival
- In accordance with maritime law, women and children had a higher probability of survival
- In general, Crew had a higher probability of survival than 3rd class passengers


